---
title: "611 Final Project"
author: "Tianyi Wang"
date: "11/9/2021"
output: word_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(lubridate)
library(dplyr)
library(DT)
knitr::opts_chunk$set(echo = TRUE)
```

# wrangling the data
rm(list=ls())

fillColor = "#FFA07A"
fillColor2 = "#F1C40F"

meets = read_csv("/Users/moyi/Desktop/powerliftingdata.csv")
powerlifting = read_csv("/Users/moyi/Desktop/powerlifting2015-2019.csv")
openpowerlifting= read_csv("/Users/moyi/Desktop/openpowerlifting.csv")


datatable(head(meets), style="bootstrap", class="table-condensed", options = list(dom = 'tp',scrollX = TRUE))
datatable(head(powerlifting), style="bootstrap", class="table-condensed", options = list(dom = 'tp',scrollX = TRUE))


# Country and Meets Data

```{r}
meets %>%
  group_by(MeetCountry) %>%
  summarise(Count = n()) %>%
  arrange(desc(Count)) %>%
  ungroup() %>%
  mutate(Country = reorder(MeetCountry,Count)) %>%
  head(10) %>%
  
  ggplot(aes(x = Country,y = Count)) +
  geom_bar(stat='identity',colour="white", fill = fillColor) +
  geom_text(aes(x = Country, y = 1, label = paste0("(",Count,")",sep="")),
            hjust=0, vjust=.5, size = 4, colour = 'black',
            fontface = 'bold') +
  labs(x = 'Country', 
       y = 'Count', 
       title = 'Country and Count') +
  coord_flip() +
  theme_bw()
```


# Most Common Weight Class Kg among Men

```{r}
powerlifting %>%
  filter(Sex == "M") %>%
  group_by(WeightClassKg) %>%
  summarise(Count =  n()) %>%
  ungroup() %>%
  mutate(WeightClassKg = reorder(WeightClassKg,Count)) %>%
  arrange(desc(Count)) %>%
  head(10) %>%
  
  ggplot(aes(x = WeightClassKg,y = Count)) +
  geom_bar(stat='identity',colour="white", fill = fillColor2) +
  geom_text(aes(x = WeightClassKg, y = 1, label = paste0(" ",Count," ",sep="")),
            hjust=0, vjust=.5, size = 4, colour = 'black',
            fontface = 'bold') +
  labs(x = 'Weight Class Kg', 
       y = 'Count', 
       title = 'Weight Class Kg and Count') +
  coord_flip() +
  theme_bw()
```


# Most Common Division among 100 kg Men Category

```{r}
powerlifting %>%
  filter(Sex == "M" & WeightClassKg == 100 & !is.na(Division)) %>%
  group_by(Division) %>%
  summarise(Count =  n()) %>%
  ungroup() %>%
  mutate(Division = reorder(Division,Count)) %>%
  arrange(desc(Count)) %>%
  head(10) %>%
  
  ggplot(aes(x = Division,y = Count)) +
  geom_bar(stat='identity',colour="white", fill = fillColor2) +
  geom_text(aes(x = Division, y = 1, label = paste0(" ",Count," ",sep="")),
            hjust=0, vjust=.5, size = 4, colour = 'black',
            fontface = 'bold') +
  labs(x = 'Division', 
       y = 'Count', 
       title = 'Most Common Division among 100 kg Men Category') +
  coord_flip() +
  theme_bw()
```


# Most Common Weight Class Kg among Women

```{r}
powerlifting %>%
  filter(Sex == "F") %>%
  group_by(WeightClassKg) %>%
  summarise(Count =  n()) %>%
  ungroup() %>%
  mutate(WeightClassKg = reorder(WeightClassKg,Count)) %>%
  arrange(desc(Count)) %>%
  head(10) %>%
  
  ggplot(aes(x = WeightClassKg,y = Count)) +
  geom_bar(stat='identity',colour="white", fill = fillColor) +
  geom_text(aes(x = WeightClassKg, y = 1, label = paste0(" ",Count," ",sep="")),
            hjust=0, vjust=.5, size = 4, colour = 'black',
            fontface = 'bold') +
  labs(x = 'Weight Class Kg', 
       y = 'Count', 
       title = 'Weight Class Kg and Count') +
  coord_flip() +
  theme_bw()
```

# The Wilks Coefficient or Wilks Formula is a coefficient that can be used to measure the strength of a powerlifter against other powerlifters despite the different weights of the lifters. Robert Wilks, CEO of Powerlifting Australia, is the author of the formula.
## We plot the highest Wilks for women

```{r}
powerlifting %>%
  filter(Sex == "F") %>%
  group_by(Name) %>%
  summarise(BestWilks =  median(Wilks,na.rm =TRUE)) %>%
  ungroup() %>%
  mutate(Name = reorder(Name,BestWilks)) %>%
  arrange(desc(BestWilks)) %>%
  head(10) %>%
  
  ggplot(aes(x = Name,y = BestWilks)) +
  geom_bar(stat='identity',colour="white", fill = fillColor2) +
  geom_text(aes(x = Name, y = 1, label = paste0(" ",round(BestWilks)," ",sep="")),
            hjust=0, vjust=.5, size = 4, colour = 'black',
            fontface = 'bold') +
  labs(x = 'Name', 
       y = 'Wilks ', 
       title = 'Name and Wilks') +
  coord_flip() +
  theme_bw() 
```

## We plot the highest Wilks for men

```{r}
powerlifting %>%
  filter(Sex == "M") %>%
  group_by(Name) %>%
  summarise(BestWilks =  median(Wilks,na.rm =TRUE)) %>%
  ungroup() %>%
  mutate(Name = reorder(Name,BestWilks)) %>%
  arrange(desc(BestWilks)) %>%
  head(10) %>%
  
  ggplot(aes(x = Name,y = BestWilks)) +
  geom_bar(stat='identity',colour="white", fill = fillColor) +
  geom_text(aes(x = Name, y = 1, label = paste0(" ",round(BestWilks)," ",sep="")),
            hjust=0, vjust=.5, size = 4, colour = 'black',
            fontface = 'bold') +
  labs(x = 'Name', 
       y = 'Wilks ', 
       title = 'Name and Wilks') +
  coord_flip() +
  theme_bw() 
```